---
title: "Title comes here"
subtitle: "Subtitle comes here"
author: "[Laurent Gatto](#laurent-gatto)"
date: "2018/01/01"
output:
  xaringan::moon_reader:
    css: ["default", "default-fonts", "my.css"]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}


options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)

library(tidyverse)
library(SBpitch)

predata <- readRDS("SifanData/predata")
rw <- readRDS("SifanData/rw")

```

class: middle, center

## Content

---
## [StasbombR Data](https://github.com/statsbomb/StatsBombR)
```{r, echo=F}
DT::datatable(head(predata), fillContainer = FALSE, options = list(pageLength = 6))
```
####Data provided by [Statsbomb](https://github.com/statsbomb/open-data)

---
## Random Walk

A path that consists of a succession of some random steps on some mathematical space.

- A point moves along the integer line

--

A random walk on the soccer filed


```{r, echo=F}
rw.test <- rw(3000, .5, .5)
```

---
## Random Walk under Harmonic Potential Function
Using potential function as a guidance for random walk

--

- A step by the random particle under a force.
$$r(t_{i+1}) - r(t_i) = - \nabla V(r(t_i)) (t_{t+1} - t_i) + \sigma \sqrt{(t_{i+1} - t_i)} Z_{i+1}$$

--
<br>

- Small_Change = Estimated_Velocity x TimeStep + Noise 