---
title: "Potential Functions and Soccer"
author: "Adhvaith, Sifan, Nick"
date: "2021/07/15"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)


knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  fig.show = TRUE,
  hiline = TRUE
)
library(tidyverse)
library(SBpitch)

predata <- readRDS("final project/sifan_pre_data/predata")
rw = readRDS("final project/random walk")
rwf = readRDS("final project/rw")
```


---
## [StasbombR Data](https://github.com/statsbomb/StatsBombR)
```{r, echo=F}
DT::datatable(head(predata), fillContainer = FALSE, options = list(pageLength = 6))
```



####Data provided by [Statsbomb](https://github.com/statsbomb/open-data)


---
## Random Walk

A sequence of some steps in random directions on some mathematical space.

- A point randomly moves along the integer line

- A point randomly moves on x-y plane

--

A random walk on the soccer filed

```{r, echo=F, warning=F, message=F}
rw
```



---

## Potential Function

- Idea: The ball is a randomly drifting ball that is attracted to the goal by some "force". 
--
<br>

<center>![](https://cdn.kastatic.org/googleusercontent/wBalF7MINVVbEksIOvIBlO6RupAqyg5yY7nkoZ5p3bPTBCGjkrWAyTQtspKaMm9BIWRlMKj089R3R15hBDI5yFY)

<br>
.footnote[]

---
## Potential Function
- We can try to model this underlying force based on the movements of the ball

--

- Our Potential Functions
  - Gravity

$$ V(x,y) = -\frac{G}{\sqrt{x^2 + y^2}} $$




---
## Random Walk under Harmonic Potential Function
Using potential function as a guidance for random walk

--

- A step by the random particle under a force.
$$r(t_{i+1}) - r(t_i) = - \nabla V(r(t_i)) (t_{t+1} - t_i) + \sigma \sqrt{(t_{i+1} - t_i)} Z_{i+1}$$

--
<br>

- Small_Change = Estimated_Velocity x TimeStep + Noise 


---